---
title: "Pkmn"
author: "Brian"
date: "August 9, 2017"
output: html_document
#runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(knitr)
library(mlr)
library(RColorBrewer)
library(jsonlite)
library(data.table)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

# Hashtag creates header
{r} = shows code + results
{r eval=FALSE} = shows code only
{r echo=FALSE} = shows results only
Embed R code in text: Value is `r 2+2` = 4 ; shows "Value is 4"

## Dependencies
```{r eval=FALSE}
library(tidyverse)
library(ggthemes)
library(knitr)
library(mlr)
library(RColorBrewer)
library(jsonlite)
```

# Load JSON from pasted text file
```{r}
pkmnjson <- fromJSON('C:/kaggle/pkmn/smogon_scrape.txt')
```


# Clean up "alts" data from JSON and binding it to original dataset
```{r}
#Create id column for joining
pkmnjson$id <- 1:nrow(pkmnjson)

#Convert alts column into dataframe and join
bind <- rbindlist(pkmnjson$alts,fill=TRUE, use.names=TRUE, idcol="id")
pkmn <- merge(x=pkmnjson,y=bind,by="id", all.y=TRUE)
remove(bind)

#Remove original alts column
pkmn$alts <- NULL

#Clean Evolutions column for Pokemon with no evolutions
pkmn$evos[pkmn$evos == "character(0)"] <- NA

#Clean formats column for Pokemon which are not in any format (mid-stage evolution)
pkmn$formats[pkmn$formats == "list()"] <- "None"
pkmn$formats[pkmn$formats == "AG"] <- "Uber"

#Convert Formats to Factor
pkmn$formats <- as.factor(unlist(pkmn$formats))
pkmn$formats <- factor(pkmn$formats,levels = c("Uber","OU","Limbo","BL","UU","BL2","RU","BL3","NU","BL4","PU","LC","None"))

#As Limbo defaults to OU when the pokemon are available, convert Limbo to OU
pkmn$formats[pkmn$formats == "Limbo"] <- "OU"

#Rename suffix column to mega, create mega dummy variable
colnames(pkmn)[which(names(pkmn) == "suffix")] <- "mega"
pkmn$mega_dummy <- pkmn$mega %>% recode_factor('Mega' = 1, .default=0)

#Create Full Name column
pkmn$fullname <- paste(pkmn$name,pkmn$mega,sep=" ")

#Create BST column
pkmn <- pkmn %>% mutate(bst = hp+atk+def+spa+spd+spe)
```

```{r}
#Load Smogon old dataset, merge Legendary column
smogon <- read.csv("C:/kaggle/pkmn/smogon.csv", stringsAsFactors = FALSE, head=TRUE)
pkmn <- merge(pkmn,smogon[,c("Name","Legendary")],by.x="name",by.y="Name",all.x=TRUE)
colnames(pkmn)[which(names(pkmn) == "Legendary")] <- "legendary"
pkmn$legendary[is.na(pkmn$legendary)] <- FALSE

##Get ndex number from Pokedex dataset
pkmndex <- read.csv("C:/kaggle/pkmn/pokemon.csv",header=TRUE,stringsAsFactors = FALSE, encoding = 'UTF8')
ndexlist <- unique(pkmndex[,c("species","ndex")])

#Remove duplicated Reverse Groudon/Kyroge Primal
ndexlist <- ndexlist[!(ndexlist$species == "Groudon" & ndexlist$ndex == 382),]
ndexlist <- ndexlist[!(ndexlist$species == "Kyogre" & ndexlist$ndex == 383),]

#Fix symbols for Nidoran-M and Nidoran-F and Farfetch'd
ndexlist$species[29] <- "Nidoran-F"
ndexlist$species[32] <- "Nidoran-M"
ndexlist$species[83] <- "Farfetch'd"

# Merge ndex with pkmn
pkmn <- merge(x=pkmn,y=ndexlist,by.x="name",by.y="species",all.x=TRUE)
pkmn <- pkmn %>% group_by(ndex) %>% arrange(ndex,fullname)
remove(ndexlist)

# Remove Smogon JSON id and replace with new unique
pkmn$id <- 1:nrow(pkmn)

#Convert legendary column to dummy factor
pkmn$legendary_dummy <- factor(ifelse(pkmn$legendary,"1","0"))

```


# K-means Clustering based on Pokemon Stats / Tier
```{r}
stat_cols <- c("hp","atk","def","spa","spd","spe","bst")
stat_cols_nobst <- c("hp","atk","def","spa","spd","spe")
actual <- pkmn$formats

set.seed(500)
kmeans1 <- kmeans(pkmn[,stat_cols],13, nstart=100, iter.max=50)
paste("kmeans1:",(kmeans1$betweenss/kmeans1$totss*100),"%",sep="")
# 13 Clusters -> between_SS / total_SS =  68.5 %
table(actual,kmeans1$cluster)

pkmn_comp <- pkmn %>% filter(formats != "LC" & formats != "None")
kmeans2 <- kmeans(pkmn_comp[,stat_cols],11, nstart=100, iter.max=50)
paste("kmeans2:",kmeans2$betweenss/kmeans2$totss*100,"%",sep="")
actual2 <- pkmn_comp$formats
table(actual2,kmeans2$cluster)
# 11 Clusters -> (between_SS / total_SS =  60.2 %) # Without None becomes 67.2%

# Combine BL tiers with tier above to reduce classes
pkmn2 <- pkmn
pkmn2$formats[pkmn2$formats == "Limbo"] <- "OU"
pkmn2$formats[pkmn2$formats == "BL"] <- "OU"
pkmn2$formats[pkmn2$formats == "BL2"] <- "UU"
pkmn2$formats[pkmn2$formats == "BL3"] <- "RU"
pkmn2$formats[pkmn2$formats == "BL4"] <- "NU"
pkmn2$formats <- factor(pkmn2$formats,levels = c("Uber","OU","UU","RU","NU","PU","LC","None"))
# Now only 8 levels

# Try Kmeans without BL tiers
kmeans3 <- kmeans(pkmn2[,stat_cols],8, nstart=100, iter.max=50)
paste("kmeans3:",kmeans3$betweenss/kmeans3$totss*100,"%",sep="")
# 8 Clusters: (between_SS / total_SS =  61.1 %)
actual3 <- pkmn2$formats
table(actual3,kmeans3$cluster)

# Try Kmeans without BL tiers and without LC/None
pkmn2_comp <- pkmn2 %>% filter(formats != "LC" & formats != "None")
pkmn2_comp$formats <- factor(pkmn2_comp$formats,levels = c("Uber","OU","UU","RU","NU","PU"))

kmeans4 <- kmeans(pkmn2_comp[,stat_cols],6, nstart=100, iter.max=50)
paste("kmeans4:",kmeans4$betweenss/kmeans4$totss*100,"%",sep="")
# 6 Clusters: (between_SS / total_SS =  47.2 %)
actual4 <- pkmn2_comp$formats
table(actual4,kmeans4$cluster)

```

# Graphing Kmeans Results
```{r}
# PCA
pkmn_pca <- prcomp(pkmn[,stat_cols], rank.=2)
pkmn_pca
eig <- (pkmn_pca$sdev)^2
var <- eig*100/sum(eig)
cumvar <- cumsum(var)
all_eig <- data.frame(eig = eig, variance = var,
                     cumvariance = cumvar)
all_eig

plot(pkmn_pca, type="l")
# Shows that first 2 PCAs account for 86% of variance already

pkmn_pca <- prcomp(pkmn[,stat_cols_nobst], rank.=5)
pkmn_pca
eig <- (pkmn_pca$sdev)^2
var <- eig*100/sum(eig)
cumvar <- cumsum(var)
all_eig <- data.frame(eig = eig, variance = var,
                     cumvariance = cumvar)
all_eig

plot(pkmn_pca, type="l")
#plot(pkmn$bst, col=kmeans1$cluster)
#centers1 <- kmeans1$centers
#ggplot(aes=)
```

# Random Forest
```{r}
#pkmn2
pkmn3 <- pkmn2[,c("ndex","name","fullname","hp","atk","def","spa","spd","spe","bst","mega_dummy","legendary_dummy","formats")]

prcomp(pkmn3[,4:12])

trainTask <- makeClassifTask(data = pkmn3[], target="formats")
```




## Loading and Previewing Dataset
```{r}
pkmndex <- read.csv("C:/kaggle/pkmn/pokemon.csv",header=TRUE,stringsAsFactors = FALSE, encoding = 'UTF8')
#glimpse(pkmn)
#summary(pkmn)
#kable(pkmn)
```

The accented e in Pokemon is showing up as "é" - find and replace with gsub
```{r}
pkmn$class <- gsub('é','e',pkmn$class)
pkmn$dex1 <- gsub('é','e',pkmn$dex1)
pkmn$dex2 <- gsub('é','e',pkmn$dex2)
#pkmn$dex1 <- gsub('’',"'",pkmn$dex1)
#pkmn$dex2 <- gsub('’',"'",pkmn$dex2)
```

Adding Generations to each Pokemon



```{r eruptions, echo=FALSE, eval=FALSE}
To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```
```{r tabsets, echo=FALSE, eval=FALSE}
## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)


Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.
```


